The Argennon Virtual Machine

### 2021-03-24 tex/avm.tex
Add note boxes
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

% Packages
%\usepackage{amsmath}
%\usepackage[a4paper]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{cleveref}
\lstset{
%  basicstyle=\ttfamily,
    mathescape
}
%\binoppenalty=99999
%\relpenalty=99999

@@

    \emph{Only public methods can be invoked by \texttt{invoke\_external} instruction.}

@@

    \emph{The reason behind this paged design is that the heap is usually persisted using a block device. A heap with
    a paged structure could expose the underlying block based nature of the persistence layer to the application
    layer. In this way, the compiler or the programmer could better optimize the code for the persistence layer.}

@@

    \emph{In the future, we may need to add special instructions for invoking interface and virtual methods...}

@@

    \emph{By using the \texttt{athrow} instruction properly, a programmer can make any method act like an atomic
    operation.}

@@

    \emph{The Argennon virtual machine has no instructions for issuing cryptographic signatures.}

@@

    \emph{Unlike heap pages, the AVM is not aware of different blocks of code area.}

@@

    \emph{Validators do not need to write the modified pages back to ZK-EDB servers. ZK-EDBs will receive the new
    block, and they will update their database by emulating the AVM execution.}

@@

    \emph{A transaction always pays all of its proposed fee, no matter how much of its predefined resources were not
    used in the final emulation.}

@@

    \emph{In a round, an honest validator never gives a receipt for an identical memory block to two different ZK-EDBs.}

@@

    \emph{One ZK-EDB server could own multiple winning tickets in a round.}

    To run this lottery, every round, based on the current block seed, a collection of \emph{valid} receipts will be
    selected randomly as the \emph{winning receipts} of the round. A receipt is \emph{valid} in the round \(r\) if:

@@

    \emph{The winners of the lottery were validators one round before the lottery round.}

@@

    The winning tickets of the lottery of the round \(r\) need to be included in the block of the round \(r\),
    otherwise they will be considered expired. Validation and prize distribution for the winning tickets of the round
    \(r\) will be done in the round \(r + 1\). This way, \textbf{the content of the challenge memory block could be
    kept secret during the lottery round.} Every winning ticket will get an equal share of the lottery prize.

>>>>

% Packages
%\usepackage{amsmath}
%\usepackage[a4paper]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{tcolorbox}
\lstset{
%  basicstyle=\ttfamily,
    mathescape
}
%\binoppenalty=99999
%\relpenalty=99999
\newcommand{\note}[1] {
    \begin{tcolorbox}[colframe=white,colback=white]
        \emph{#1}
        %\emph{#1}\medskip
    \end{tcolorbox}
}

@@

    \note{Only public methods can be invoked by \texttt{invoke\_external} instruction.}

@@

    \note{The reason behind this paged design is that the heap is usually persisted using a block device. A heap with
    a paged structure could expose the underlying block based nature of the persistence layer to the application
    layer. In this way, the compiler or the programmer could better optimize the code for the persistence layer.}

@@

    \note{In the future, we may need to add special instructions for invoking interface and virtual methods...}

@@

    \note{By using the \texttt{athrow} instruction properly, a programmer can make any method act like an atomic
    operation.}

@@

    \note{The Argennon virtual machine has no instructions for issuing cryptographic signatures.}

@@

    \note{Unlike heap pages, the AVM is not aware of different blocks of code area.}

@@

    \note{Validators do not need to write the modified pages back to ZK-EDB servers. ZK-EDBs will receive the new
    block, and they will update their database by emulating the AVM execution.}

@@

    \note{A transaction always pays all of its proposed fee, no matter how much of its predefined resources were not
    used in the final emulation.}

@@

    \note{In a round, an honest validator never gives a receipt for an identical memory block to two different ZK-EDBs.}

@@

    \note{One ZK-EDB server could own multiple winning tickets in a round.}

    To run this lottery, every round, based on the current block seed, a collection of \emph{valid} receipts will be
    selected randomly as the \emph{winning receipts} of the round. A receipt is \emph{valid} in round \(r\) if:

@@

    \note{The winners of the lottery were validators one round before the lottery round.}

@@

    The winning tickets of the lottery of round \(r\) need to be included in the block of the round \(r\),
    otherwise they will be considered expired. Validation and prize distribution for the winning tickets of round
    \(r\) will be done in the round \(r + 1\). This way, \textbf{the content of the challenge memory block could be
    kept secret during the lottery round.} Every winning ticket will get an equal share of the lottery prize.
